Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-15 chi2012.tex
updated design figure

\section{Designing DataPalette : An Interface for Serendipitous Data Mixing}
\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=18cm]{img/screenshot}
\caption{WebBox uses a Drag and Drop interface to add data into the workspace.}
\label{fig:dragdrop}
\end{center}
\end{figure*}

@@

\subsection{Interaction mechanisms for data mixing}
In order to familiar to new users, we borrowed the overall interaction and feel from MacOS Finder-style file managers, with support for separate windows which can be freely moved, resized and titled. (As described in Results, we discovered that windows caused considerable clutter and frustration in later stages of some tasks, a fact we did not detect during prototype testing.)  Instead of files, however, the element of manipulation was a single, discrete structured data item, or \emph{instance}.  (In order to do this, non-RDF data had to be first ``chunked'' into instances, which was usually a well-defined process).  Data sources were represented as collapsable panels in a sidebar on the left of the workspace, from which instances or entire data sources could be ``pulled off'' onto the workspace.  Figure \

>>>>

\section{Designing DataPalette : An Interface for Serendipitous Data Mixing}
\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=18cm]{img/screenshot}
\caption{DataPalette Workspace, a file manager-inspired Drag and Drop interface for structured data mixing. Collapsable displays of data sources are listed on the left, from which instances or entire sets of items can be dragged to form a windoow (group) on the workspace.}
\label{fig:workspace}
\end{center}
\end{figure*}

@@

\subsection{Interaction mechanisms for data mixing}
In order to familiar to new users, we borrowed the overall interaction and feel from MacOS Finder-style file managers, with support for separate windows which can be freely moved, resized and titled. (We later discovered that windows caused considerable clutter at the later stages of some tasks, a fact we did not detect until the main study as we describe later.)  Instead of files, however, the element of manipulation was a single, discrete structured data item, or \emph{instance}.  In order to define \emph{instances} for non-RDF data, such as JSON or XML, we defined all subtrees with more than 1 child as its an instance.  Data sources were represented as collapsable panels in a sidebar on the left of the workspace, from which instances or entire data sources could be ``pulled off'' onto the workspace.  Figure \
